Genome-wide changes in expression during inflorescence architecture development

### 2015-08-14 ms.Rmd
re-run with maxClust = 25; output maxClust

library(data.table)
library(ggplot2)
extrafont::loadfonts()

@@

@@

```{r mfuzz}
expressionMatrix <- readRDS('output/cutadapt-2015-07-29/STAR-2015-07-29/DESeq2-2015-08-04/mfuzz-2015-08-05/expressionMatrix.Rds')
c1 <- readRDS('output/cutadapt-2015-07-29/STAR-2015-07-29/DESeq2-2015-08-04/mfuzz-2015-08-05/c1.Rds')
memCutoff <- 0.5

# get clusters and membership
cluster <- data.table(id = names(c1$cluster), Cluster = c1$cluster, Membership = apply(c1$membership, 1, max), key = "id")

# get standardised VST counts
exprs <- data.table(Biobase::exprs(expressionMatrix), keep.rownames = TRUE, key = "rn")

# set up cluster labels
numGenes <- cluster[Membership > 0.5, .(number = length(id)), by = Cluster]
setkey(numGenes, 'Cluster')
clustLabels <- numGenes[, paste0("Cluster ", Cluster, "\n(", number, " genes)")]

# merge clusters with expression values
plotData.wide <- cluster[exprs]

# make long
plotData <- reshape2::melt(plotData.wide[ Membership > memCutoff ], id.vars = c('id', 'Cluster', 'Membership'), variable.name = 'Stage', value.name = "Normalised, transformed read counts")

# add cluster labels
plotData[, Cluster := plyr::mapvalues(as.factor(Cluster), seq(1, length(unique(Cluster))), clustLabels)]

# fix stage label
plotData[, Stage := plyr::mapvalues(Stage, "ePBM.SBM", "ePBM/SBM")]

# set up heatscale
heatscale <- RColorBrewer::brewer.pal(n = 6, name = "YlOrRd")

# add centres
centres.wide <- data.table(c1$centers, Cluster = clustLabels)
centres <- reshape2::melt(centres.wide, id.vars = 'Cluster', variable.name = 'Stage', value.name = "Normalised, transformed read counts")
centres[, Stage := plyr::mapvalues(Stage, "ePBM.SBM", "ePBM/SBM")]

# number of clusters (for text)
c <- length(unique(c1$cluster))

f_mfuzzClusters <- ggplot(plotData, aes(x = Stage, y = `Normalised, transformed read counts`,
                     colour = Membership, group = id)) +
  theme_minimal(base_size = 8, base_family = "Helvetica") +
  xlab(NULL) +
  scale_colour_gradientn(colours = heatscale, limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  geom_line() +
  geom_line(data = centres, mapping = aes(group = 1), colour = "black", alpha = 0.5) +
  facet_wrap(~ Cluster)

figCount <- incCount(figCount, "f_mfuzzClusters")
```

>>>>

@@

source('src/R/figures.R')

@@

```{r mfuzz}
figCount <- incCount(figCount, "f_mfuzzClusters")
```
